### 2022-11-13 sections/oxf_refs.tex
Create oxf_refs.tex

\cvsection{References}

@@

\begin{itemize}
\item[]{\small {\bfseries Petra Schleiter}, Professor of Comparative Politics, University of Oxford, UK}
\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:petra.schleiter@politics.ox.ac.uk}{\textcolor{blue}{petra.schleiter@politics.ox.ac.uk}}}} \vspace{1.5mm}
\item[]{\small {\bfseries Gonzalo Delamaza}, Full Professor, Universidad de Los Lagos, Chile}
\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:gonzalo.delamaza@ulagos.cl}{\textcolor{blue}{gonzalo.delamaza@ulagos.cl}}}} \pagebreak %% \vspace{1.5mm}
\item[]{\small {\bfseries Miguel \'Angel L\'opez}, Assistant Professor, Universidad de Chile, Chile}
\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:mlopez@uchile.cl}{\textcolor{blue}{mlopez@uchile.cl}}}} \vspace{1.5mm}
\item[]{\small {\bfseries Alfredo Joignant}, Full Professor, Universidad Diego Portales, Chile}
\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:alfredo.joignant@mail.udp.cl}{\textcolor{blue}{alfredo.joignant@mail.udp.cl}}}} \vspace{1.5mm}
\item[]{\small {\bfseries Jaime Baeza}, Assistant Professor, Universidad de Chile, Chile}
\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:jbaezaf@u.uchile.cl}{\textcolor{blue}{jbaezaf@u.uchile.cl}}}} \vspace{1.5mm}
\item[]{\small {\bfseries Marcel Thez\'a}, Associate Professor, Universidad de Los Lagos, Chile}
\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:marcel.theza@ulagos.cl}{\textcolor{blue}{marcel.theza@ulagos.cl}}}} \vspace{1.5mm}
\end{itemize}

>>>>

\cvsection{Referees}

@@

\begin{itemize}
\item[]{\small {\bfseries Petra Schleiter}, Professor of Comparative Politics, University of Oxford, UK}
\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:petra.schleiter@politics.ox.ac.uk}{\textcolor{blue}{petra.schleiter@politics.ox.ac.uk}}}} \vspace{1.5mm}
\item[]{\small {\bfseries David Doyle}, Professor of Politics, University of Oxford, UK}
\item[]{\vspace{-1mm}\textcolor{oxfordblue}{\faEnvelope} \hspace{0.1mm} {\small \href{mailto:david.doyle@politics.ox.ac.uk}{\textcolor{blue}{david.doyle@politics.ox.ac.uk}}}} \vspace{1.5mm}
\end{itemize}
